\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{setspace}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{titlesec}


\usepackage{microtype}
\SetTracking{encoding=*}{115}


\titleformat{\section}{\normalfont\fontsize{16pt}{18pt}\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\fontsize{14pt}{16pt}\bfseries}{\thesubsection}{1em}{}


\begin{document}

\begin{center}
    \Large \textbf{Untrade Mid Term Report} \\
    \normalsize \textbf{Team 41}
\end{center}

\section{Progress Update}
1. Briefly describe the current status of your trading strategy development on btcusdt and ethusdt.\\
2. Mention any challenges faced and how you overcame them.


\section{Strategy Overview}
1. Describe your trading strategy's core concept and objectives.\\ 
2. Outline the key features and indicators used and what purpose do they serve? How do they correlate with trend , momentum , volume and volatility?


\section{Performance Metrics}
 1. Provide a summary of your strategy's performance metrics for the past 4 years: - Profit/Loss - Sharpe Ratio - Maximum Drawdown - Annualized Returns -Time to recovery\\ 
 2. Include visualizations (e.g., equity curve, drawdown chart)



\section{Unique Approaches and Innovations}
1. Describe any unique or innovative aspects of your strategy. Are there any particular inefficiency or market anomalies directly or indirectly linked to the unique approach that you adopted? \\
2. Explain how your approach differs from traditional methods of trading. Is there any novel mathematical model that you have applied in this present approach? 

\section{Next Plan}
Any transition process that is already planned since the present algorithm is not competitive enough and you wish to make updates or move altogether to a different approach before the final round. A small overview of it should be attached with mid term report. 

\end{document}
